---
title: "Mpox Project"
author: "Shayne Estill"
output: github_document
---


```{r}
library(janitor)
library(rio)
library(lubridate)
library(skimr)
library(epikit)
library(gtsummary)
library(apyramid)
library(tidyverse)
library(pacman)
library(readxl)
```

```{r}
# Install remotes if you need to (so you can install a package from GitHub)
pacman::p_load("remotes")

# Use the install_github function from remotes to install appliedepidata
remotes::install_github("appliedepi/appliedepidata")
```

```{r}
# Save down the two mpox files using the save_data() function from appliedepidata
appliedepidata::save_data("mpox_linelist",
                        path = "data")

appliedepidata::save_data("mpox_aggregate_table",
                          path = "data")
```

Read the data into this file
```{r}
mpox_table = read_csv(file = "./data/mpox_aggregate_table.csv")

mpox_linelist = read_excel("./data/mpox_linelist.xlsx")
```

Data exploration
Tasks: Take a look at the different data frames and determine:

- The number of columns and observations (e.g. their dimensions)
- The class of their columns and whether it matches its nature (e.g., are “dates” considered “dates” by R?)
- If the contents of columns are clean and standardized in the mpox linelist (e.g. gender, clinical symptoms, outcome, hiv status and sexual orientation). Do you need to recode any of them?
- How unknown or missing data is categorized in these columns. Do these values need to be standardized?
```{r}
mpox_table = 
    janitor::clean_names(mpox_table)

mpox_linelist = 
    janitor::clean_names(mpox_linelist)
```

The mpox_table dataset has `r nrow(mpox_table)` rows and `r nrow(mpox_table)` columns. 

The mpox_linelist dataset has `r nrow(mpox_linelist)` rows and `r nrow(mpox_linelist)` columns. 